A Comparative Quality Metric for Fuzzing with Logic State Coverage

### 2024-03-10 paper/main.tex
paper: discussion: quality metric for general fuzzing

% FIXME: revise!
\pp{Quality metric for general fuzzing}
%
The legitimacy of logic state coverage hinges on the current conventional
understanding of interesting program behaviors in \emph{untargeted} fuzzing,
namely the behaviors with less repetition. However, recent findings 
\cite{regression,risk,root-causes-age} suggest that various code characteristics
(e.g., the age of code) make some code likelier to cause bugs,
which makes the program behaviors executing such a portion of code have a higher
expectation to reveal unknown abnormal behaviors (i.e., more interesting).
%
\emph{Targeted} fuzzing \cite{regression,directed,risk} attempts to capitalize
the findings by prioritizing such code, while logic state coverage would
under-estimate their quality by only considering less repetition as more
interesting.

For a quality metric that encompasses general (i.e., both untargeted and
targeted) fuzzing, future research needs to address two issues around
interestingness. First, it should refine the interestingness of program
behaviors. Not only should it systemize the factors that decide interestingness,
but also it should assess which factor affects \emph{more} than others by
\emph{how much}.  Second, it should incorporate such refined interestingness
into the quality metric. If it would follow the philisophy of logic state
coverage (i.e., more uninteresting behavior in fewer logic states),
\emph{grouping} uninteresting branches can be an approach as it makes the
program behaviors with uninteresting branches occupy fewer logic states.

>>>>

% FIXME: revise!
\pp{Quality metric for general fuzzing}
%
Logic state coverage evaluates the quality of \emph{untargeted} fuzzing, where
the program behaviors with less repetition are generally deemed more
interesting. 
%
However, \emph{targeted} fuzzing
\cite{aflchurn,chen2020savior,osterlund2020parmesan,lee2024syzrisk} attempts to
capitalize the recent findings \cite{aflchurn,zhai2022ndss,nikolaos2022longvuln}
that some code such as recent patches are potentially \emph{more interesting}
(i.e., likelier to cause abnormal behaviors), which may render logic state
coverage to under-estimate targeted fuzzing by overlooking potentially
interesting behaviors.

To devise a quality metric that is also compatible to targeted fuzing, future
research may need to address two issues revolving around interestingness. First,
it should accurately describe the interestingness in an unpartial way (i.e., not
favoring a certain fuzzer or setting). To do so, it should assess which factor
affects interestingness and how much more than one another. Second, it should
incorporate such a description into the quality metric. Should it follow the
philisophy of logic state coverage, grouping uninteresting behaviors may be a
possible approach to make them less significant.
